Differentiable Neural Computers

### 2018-05-06 Presentation/Presentation.tex
minor fixes

\begin{frame}{Introduction: RNNs}
	\begin{minipage}[t]{.44\textwidth}	
	\alert{Simple Neural Net}
	\begin{figure}[h!]
	\vspace{6.5pt}
	\begin{tikzpicture}[scale=.5]
		\foreach \y /\alph/\name in {
			0/x1/$x_1$,
		  	-1/x2/$x_2$,
		  	-2/x3/$x_3$,
		  	-4/xM/$x_M$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (x..) at (0,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			1/h1/$h_1$,
		  	0/h2/$h_2$,
		  	-1/h3/$h_3$,
		  	-5/hN/$h_N$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (h..) at (4,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			0/y1/$y_1$,
		  	-1/y2/$y_2$,
		  	-2/y3/$y_3$,
		  	-4/yP/$y_P$
		 }{
		 	\node[circle, draw=gray!90,inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (y..) at (8,-3) {\tiny {\vdots}};
		 \foreach \x in {x1, x2, x3, xM}
		 {\foreach \h in {h1, h2, h3, hN}
		 {\draw (\x) edge[gray!90] (\h);}}
		 \foreach \x in {h1, h2, h3, hN}
		 {\foreach \y in {y1, y2, y3, yP}
		 {\draw (\x) edge[gray!90] (\y);}}
	\end{tikzpicture}
	\end{figure}
	\vspace{10pt}
	\centering
	\small \alert{$y=g(h),\ h=f(x)$}\\
	No memory
	\end{minipage}
	\pause
	\hspace{1cm}
	\begin{minipage}[t]{.44\textwidth}	
	\alert{Simple Recurrent Net}
	\begin{figure}[h!]
	\begin{tikzpicture}[scale=.5]
		\foreach \y /\alph/\name in {
			0/x1/$x_1$,
		  	-1/x2/$x_2$,
		  	-2/x3/$x_3$,
		  	-4/xM/$x_M$
		 }{
		% 	\node[] (\alph) at (0,\y) {\name};
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (x..) at (0,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			1/h1/$h_1$,
		  	0/h2/$h_2$,
		  	-1/h3/$h_3$,
		  	-5/hN/$h_N$
		 }{
		 	\node[circle, draw=mLightBrown, inner sep=0pt,minimum size=3mm,fill=gray!20] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (h..) at (4,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			0/y1/$y_1$,
		  	-1/y2/$y_2$,
		  	-2/y3/$y_3$,
		  	-4/yP/$y_P$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (y..) at (8,-3) {\tiny {\vdots}};
		 \foreach \x in {x1, x2, x3, xM}
		 {\foreach \h in {h1, h2, h3, hN}
		 {\draw (\x) edge[gray!90] (\h);}}
		 \foreach \x in {h1, h2, h3, hN}
		 {\foreach \y in {y1, y2, y3, yP}
		 {\draw (\x) edge[gray!90] (\y);}}
		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(0.8,0.8) and +(-0.8,0.8) .. (h1.west);
		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(0.4,-0.8) and +(-0.4,0.8) .. (h2.west);
		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(1,-1.6) and +(-0.6,0.4) .. (h3.west);
		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(2,-2) and +(-2,2) .. (hN.west);
	\end{tikzpicture}
	\end{figure}
	\vspace{10pt}
	\centering
	\small{ \alert{$h(t)=f([x(t); h(t-1)])$}}\\
	Finite, non-contiguous memory
	\end{minipage}
	\pause

	\begin{quote}
	\small \textit{"If training vanilla neural nets is optimization over functions, training recurrent nets is \alert{optimization over programs.}"}
	\end{quote}
\end{frame}

\begin{frame}{Approach}
	Train a RNN to act as a \alert{controller} to interact with a memory matrix M of N (arbitrary many) addresses.
	\pause
	\begin{enumerate}
	\item \alert{Content Lookup}\\
		\begin{itemize}
		\item \alert{Attention} over memory defined by weightings $W \in \mathbb{R}^N$
		\item Compare controller output with memory objects (\alert{auto-associative memory})
		\item Allow partial matches  (\alert{pattern completion})
		\end{itemize}
	\pause
	\item \alert{Sequential Retrieval}
		\begin{itemize} 
		\item Fill $L \in \{0,1\}^{2N}$ indexing \alert{temporal transitions}
		\item \alert{Shift} operations defined by $LW,\ L^TW$
		\end{itemize}
	\pause
	\item \alert{Dynamic Allocation}
		\begin{itemize}
		\item Mark memory locations with $\{0,1\}$ to \alert{signal usage}
		\item Manipulate signals during R/W operations to enable \alert{reallocation}
		\item Generalization to \alert{unbounded memory}
		\end{itemize}
	\end{enumerate}
\end{frame}

\begin{frame}{Controller}
	A deep \alert{long short-term memory network} receiving input:
	\[
	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots ;\pmb{r}_{t-1}^R]
	\]
	and producing output:
	\[
	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
	\]
	where $\mathcal{N}$ a set of state equations and $\vartheta$ their trainable parameters.
\end{frame}

@@

\begin{frame}{Controller: Signal-Flow}
	\alert{Single LSTM layer}
	\begin{figure}
	\begin{tikzpicture}[scale=0.5]
		%-------------------------------------------------------------------------------
		% LSTM
		%-------------------------------------------------------------------------------
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{mDarkTeal}{$;$}};

@@

\begin{frame}{Controller: Full View}
	\alert{LSTM Network} (multiple layers)
	\begin{figure}
	\begin{tikzpicture}[scale=1]
	\tikzset{miniLSTM/.style={draw=black, fill=white, minimum width=20pt, minimum height=10pt, thick}}
	\tikzset{split/.style={circle, draw=black,inner sep=0pt, minimum size = 3mm, fill=white}}
		\node (dummy_node) at (0,0) {};
		\foreach \name/\x in {x1/2, x2/4, x3/6, xd/8, xL/10} {\node[inner sep=0] (\name) at (\x,0) {};}
		\foreach \name/\x in {h1/3, h2/5, h3/7, hL/10} {\node[inner sep=0] (\name) at (\x, -2) {};}
		\foreach \name/\x in {s0/3, s1/5, s2/7, sL/10} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
		\foreach \name/\x/\tag in {L1/2/$LSTM_1$, L2/4/$LSTM_2$, L3/6/$LSTM_3$, LL/10/$LSTM_L$} 
		{\node[miniLSTM] (\name) at (\x,-2) {\textcolor{black}{\tiny\tag}};}
		\node (Ld) at (8,-2) {$\dots$};
		\node (sd) at (8,-3) {$\dots$};
		\draw (dummy_node) -| (LL);
		\draw (L1) edge[->] (L2);
		\draw (L2) edge[->] (L3);
		\draw (L3) edge[->] (Ld);
		\draw (Ld) edge[->] (LL);
		\draw[->] (x1) edge (L1.north);
		\draw[->] (x2) edge (L2.north);
		\draw[->] (x3) edge (L3.north);
		\draw[->] (xL) edge (LL.north);
		\draw[->] (xd) edge (Ld.north);
		\draw[->] (1,0) |- (s0);
		\draw[->] (h1) edge (s0);
		\draw[->] (s0) edge (s1);
		\draw[->] (h2) edge (s1);
		\draw[->] (h3) edge (s2);
		\draw[->] (s1) edge (s2);
		\draw[->] (s2) edge (sd);
		\draw[->] (sd) edge (sL);
		\draw[->] (LL) edge (sL);		
		\draw[->] (sL) edge (10, -5);
		% labels
		\node[label=above right :$\scriptsize\textcolor{white}{\xx_t}$] (xt) at (0,0) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^1}$] (xt) at (3,-2) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^2}$] (xt) at (5,-2) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^3}$] (xt) at (7,-2) {};
		\node[label=below :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1]}$] (xt) at (4,-3) {};
		\node[label=below :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1;\hh_t^2]}$] (xt) at (6,-3) {};
		\node[label=left :$\scriptsize\textcolor{white}{[\xx_t;\hh_t^1;\dots;\hh_t^L]}$] (xt) at (10,-5) {};
	\end{tikzpicture}
	\end{figure}
\end{frame}

@@

	\pause
	\alert{Intermediate output} $\pmb{\upsilon}_t$
	\[
	\pmb{y}_t = \pmb{\upsilon}_t + W_R[\pmb{r}_t^1;\dots;\pmb{r}_t^R] \tag{\alert{Memory-conditioning}}
	\]

	\pause
	\alert{Interface vector} $\pmb\xi_t$

@@

\begin{frame}{Memory Adressing: RW}
\alert{Read operations}
\[
\pmb{r}_t^i = M_t^T\pmb{w}_t^{r,i}
\]
\pause
\alert{Write operations}
\[
M_t = M_{t-1} \circ (\pmb{1} - \pmb{w}_t^T\pmb{e}_t^T) + \pmb{w}_t^W\pmb{v}_t^T
\]
\end{frame}

\begin{frame}{Further Reading}
	\begin{itemize}
	\item \alert{Neural Turing Machines} (Graves, Wayne, Danihelka)
	\item \alert{Entity Networks} (Henaff, Weston, Szlam, Bordes, LeCun)
	\item \alert{Principles of Probabilistic Programming Languages} (Goodman)
	\item \alert{Backprop as a Functor} (Fong, Spivak, Tuyéras)
	\item \alert{Formal Methods for Probabilistic Programming} (Selsam, Liang, Dill)
	\end{itemize}
\end{frame}

>>>>

\begin{frame}{Introduction: RNNs}
	\begin{minipage}[t]{.44\textwidth}	
	\alert{Simple Neural Net}
	\begin{figure}[h!]
	\vspace{6.5pt}
	\begin{tikzpicture}[scale=.5]
		\foreach \y /\alph/\name in {
			0/x1/$x_1$,
		  	-1/x2/$x_2$,
		  	-2/x3/$x_3$,
		  	-4/xM/$x_M$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (x..) at (0,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			1/h1/$h_1$,
		  	0/h2/$h_2$,
		  	-1/h3/$h_3$,
		  	-5/hN/$h_N$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (h..) at (4,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			0/y1/$y_1$,
		  	-1/y2/$y_2$,
		  	-2/y3/$y_3$,
		  	-4/yP/$y_P$
		 }{
		 	\node[circle, draw=gray!90,inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (y..) at (8,-3) {\tiny {\vdots}};
		 \foreach \x in {x1, x2, x3, xM}
		 {\foreach \h in {h1, h2, h3, hN}
		 {\draw (\x) edge[gray!90] (\h);}}
		 \foreach \x in {h1, h2, h3, hN}
		 {\foreach \y in {y1, y2, y3, yP}
		 {\draw (\x) edge[gray!90] (\y);}}
	\end{tikzpicture}
	\end{figure}
	\vspace{10pt}
	\centering
	%\small \alert{$y=g(h),\ h=f(x)$}\\
	\small $NN: \pmb{x}_{t_i} \mapsto \pmb{y}_{t_i}$\\
	\alert{No memory}
	\end{minipage}
	\pause
	\hspace{1cm}
	\begin{minipage}[t]{.44\textwidth}	
	\alert{Simple Recurrent Net}
	\begin{figure}[h!]
	\begin{tikzpicture}[scale=.5]
		\foreach \y /\alph/\name in {
			0/x1/$x_1$,
		  	-1/x2/$x_2$,
		  	-2/x3/$x_3$,
		  	-4/xM/$x_M$
		 }{
		% 	\node[] (\alph) at (0,\y) {\name};
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (x..) at (0,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			1/h1/$h_1$,
		  	0/h2/$h_2$,
		  	-1/h3/$h_3$,
		  	-5/hN/$h_N$
		 }{
		 	\node[circle, draw=mLightBrown, inner sep=0pt,minimum size=3mm,fill=gray!20] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (h..) at (4,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			0/y1/$y_1$,
		  	-1/y2/$y_2$,
		  	-2/y3/$y_3$,
		  	-4/yP/$y_P$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (y..) at (8,-3) {\tiny {\vdots}};
		 \foreach \x in {x1, x2, x3, xM}
		 {\foreach \h in {h1, h2, h3, hN}
		 {\draw (\x) edge[gray!90] (\h);}}
		 \foreach \x in {h1, h2, h3, hN}
		 {\foreach \y in {y1, y2, y3, yP}
		 {\draw (\x) edge[gray!90] (\y);}}
		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(0.8,0.8) and +(-0.8,0.8) .. (h1.west);
		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(0.4,-0.8) and +(-0.4,0.8) .. (h2.west);
		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(1,-1.6) and +(-0.6,0.4) .. (h3.west);
		 \draw (h1.east) [->, densely dotted, thick, mLightBrown] .. controls +(2,-2) and +(-2,2) .. (hN.west);
	\end{tikzpicture}
	\end{figure}
	\vspace{10pt}
	\centering
	%\small{ \alert{$h(t)=f([x(t); h(t-1)])$}}\\
	\small{ $RNN: \pmb{x}_{t_0} \otimes \pmb{x}_{t_1} \otimes \dots \otimes \pmb{x}_{t_i} \mapsto \pmb{y}_{t_i}$}\\
	\alert{Finite memory}
	\end{minipage}
	\pause

	\begin{quote}
	\small \textit{"If training vanilla neural nets is optimization over functions, training recurrent nets is \alert{optimization over programs}."}
	\end{quote}
\end{frame}

\begin{frame}{Approach}
	Train a RNN to act as the \alert{controller} of a memory matrix M of N 
	addresses through R \alert{read heads} and one \alert{write head}.

	\pause
	\begin{enumerate}
	\item \alert{Content Lookup}\\
		\begin{itemize}
		\item \alert{Attention} over memory defined by weightings $W \in \mathbb{R}^N$
		\item Compare controller output with memory objects (\alert{auto-associative memory})
		\item Allow partial matches  (\alert{pattern completion})
		\end{itemize}
	\pause
	\item \alert{Sequential Retrieval}
		\begin{itemize} 
		\item Fill $L \in [0,1]^{2N}$ indexing \alert{temporal transitions}
		\item \alert{Shift} operations defined by $LW,\ L^TW$
		\end{itemize}
	\pause
	\item \alert{Dynamic Allocation}
		\begin{itemize}
		\item Mark memory locations with $\{0,1\}$ to \alert{signal usage}
		\item Manipulate signals during R/W operations to enable \alert{reallocation}
		\item Generalization to \alert{unbounded memory}
		\end{itemize}
	\end{enumerate}
\end{frame}

\begin{frame}{Controller: Overview}
	A deep \alert{long short-term memory network} receiving input:
	\[
	\xx_t=[ \pmb{x}_t; \pmb{r}_{t-1}^1; \dots ;\pmb{r}_{t-1}^R]
	\]
	and producing output:
	\[
	(\pmb{\upsilon}_t,\pmb{\xi}_t)=\mathcal{N}([\xx_1;\dots;\xx_T];\vartheta)
	\]
	where $\mathcal{N}$ a set of state equations and $\vartheta$ their trainable parameters.
\end{frame}

@@

\begin{frame}{Controller: Signal-Flow (1/2)}
	\alert{Single LSTM layer}
	\begin{figure}
	\begin{tikzpicture}[scale=0.5]
		%-------------------------------------------------------------------------------
		% LSTM
		%-------------------------------------------------------------------------------
		\node[circle, inner sep=0pt,minimum size=3mm,fill=white] (conc) 
			at (-0,6) {\textcolor{mDarkTeal}{$;$}};

@@

\begin{frame}{Controller: Signal-Flow (2/2)}
	\alert{LSTM Network} (multiple layers)
	\begin{figure}
	\begin{tikzpicture}[scale=1]
	\tikzset{miniLSTM/.style={draw=black, fill=white, minimum width=20pt, minimum height=10pt, thick}}
	\tikzset{split/.style={circle, draw=black,inner sep=0pt, minimum size = 3mm, fill=white}}
		\node (dummy_node) at (0,0) {};
		\foreach \name/\x in {x1/2, x2/4, x3/6, xd/8, xL/10} {\node[inner sep=0] (\name) at (\x,0) {};}
		\foreach \name/\x in {h1/3, h2/5, h3/7, hL/10} {\node[inner sep=0] (\name) at (\x, -2) {};}
		\foreach \name/\x in {s1/5, s2/7, sL/10} {\node[split] (\name) at (\x,-3) {$\textcolor{black}{\tiny;}$};}
		\foreach \name/\x/\tag in {L1/2/$LSTM_1$, L2/4/$LSTM_2$, L3/6/$LSTM_3$, LL/10/$LSTM_L$} 
		{\node[miniLSTM] (\name) at (\x,-2) {\textcolor{black}{\tiny\tag}};}
		\node (Ld) at (8,-2) {$\dots$};
		\node (sd) at (8,-3) {$\dots$};
		\draw (dummy_node) -| (LL);
		\draw (L1) edge[->,thick] (L2);
		\draw (L2) edge[->,thick] (L3);
		\draw (L3) edge[->,thick] (Ld);
		\draw (Ld) edge[->,thick] (LL);
		\draw[->,thick] (x1) edge (L1.north);
		\draw[->,thick] (x2) edge (L2.north);
		\draw[->,thick] (x3) edge (L3.north);
		\draw[->,thick] (xL) edge (LL.north);
		\draw[->,thick] (xd) edge (Ld.north);
		%\draw[->,thick] (1,0) |- (s0);
		\draw[->,thick] (h1) |- (s1);
		\draw[->,thick] (h2) edge (s1);
		\draw[->,thick] (h3) edge (s2);
		\draw[->,thick] (s1) edge (s2);
		\draw[->,thick] (s2) edge (sd);
		\draw[->,thick] (sd) edge (sL);
		\draw[->,thick] (LL) edge (sL);		
		\draw[->,thick] (sL) edge (10, -5);
		% labels
		\node[label=above right :$\scriptsize\textcolor{white}{\xx_t}$] (xt) at (0,0) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^1}$] (xt) at (3,-2) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^2}$] (xt) at (5,-2) {};
		\node[label=above :$\scriptsize\textcolor{white}{\hh_t^3}$] (xt) at (7,-2) {};
		\node[label=below :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2]}$] (xt) at (6,-3) {};
		\node[label=left :$\scriptsize\textcolor{white}{[\hh_t^1;\hh_t^2;\dots;\hh_t^L]}$] (xt) at (10,-5) {};
	\end{tikzpicture}
	\end{figure}
\end{frame}

@@

	\pause
	\alert{Intermediate output} $\pmb{\upsilon}_t = W_y[\hh_t^1;\dots;\hh_t^L]$
	\[
	\pmb{y}_t = \pmb{\upsilon}_t + W_R[\pmb{r}_t^1;\dots;\pmb{r}_t^R] \tag{\alert{Memory-conditioning}}
	\]

	\pause
	\alert{Interface vector} $\pmb{\xi}_t = W_\xi[\hh_t^1;\dots;\hh_t^L]$

@@

\begin{frame}{Memory Adressing: Content-Lookup}
	\alert{R read keys} $\pmb{k}^{r,i} \in \mathbb{R}^W,\ i=1\dots R$\\
	\alert{R read strengths} $\beta^{r,i} \in [1,\infty),\ i=1\dots R$\\
	\alert{Write key} $\pmb{k}^{w} \in \mathbb{R}^W$\\
	\alert{Write strength} $\beta^{w} \in [1,\infty)$

	\pause
	\alert{Weightings} $w$ given by $\mathcal{C}$
	\[
	\mathcal{C}(M,\pmb{k},\beta)[i]= 
	\frac {exp \{ \mathcal{D} (\pmb{k},M[i,:])\beta \} }
	{ \sum_{j}{exp \{ \mathcal{D} (\pmb{k},M[j,:])\beta \}}}
	\]

	\pause
	\alert{Read operations}
	\[
	\pmb{r}_t^i = M_t^T\pmb{w}_t^{r,i}
	\]
	\alert{Write operations}
	\[
	M_t = M_{t-1} \circ (\pmb{1} - \pmb{w}_t^w\pmb{e}_t^T) + \pmb{w}_t^w\pmb{v}_t^T
	\]
\end{frame}

\begin{frame}{Further Reading}
	\begin{itemize}
	\item \alert{Neural Turing Machines} (Graves, Wayne, Danihelka)
	\item \alert{Entity Networks} (Henaff, Weston, Szlam, Bordes, LeCun)
	\item \alert{End-to-End Memory Networks} (Sukhbaatar, Szlam, Weston, Fergus)	
	\item \alert{Jointly Learning to Align and Translate} (Bahdanau, Cho, Bengio)
	\item \alert{Principles of Probabilistic Programming Languages} (Goodman)
	\item \alert{Backprop as a Functor} (Fong, Spivak, Tuyéras)
	\item \alert{Formal Methods for Probabilistic Programming} (Selsam, Liang, Dill)
	\end{itemize}
\end{frame}
